PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-24 paper/sec-results.tex
added references

\paragraph{Experimental measurements and process features.}
We select the single-differential invariant mass distribution of the
lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of-mass
energy of \SI{7}{\tera\electronvolt} in the high-mass region
($M_{\ell\bar\ell}>\SI{116}{\giga\electronvolt}$)~\cite{Aad:2013iua}.
We also select the single-differential rapidity distribution, $y_{\ell\bar\ell}$, in slices of
the invariant mass of the lepton pair, $M_{\ell\bar\ell}$,
measured by the CMS experiment at a centre-of-mass energy of
\SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}.
These measurements are currently included as standard in the
NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
although with appropriate kinematic cuts that remove the bins at the largest
values of invariant mass, where EW corrections become sizeable. As explained in
section~\ref{sec:pineappl-example}, 
the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
QCD contribution is $\mathcal{O}(\alphas\alpha^2)$, while the EW contribution
is $\mathcal{O}(\alpha^3)$. Our NLO QCD computation includes the
$\mathcal{O}(\alpha^2)$ and $\mathcal{O}(\alphas\alpha^2)$ contributions, while
our NLO QCD+EW computation includes the $\mathcal{O}(\alpha^2)$, 
$\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$ contributions.
Combined QCD--EW corrections occur only at NNLO, and are therefore not
considered here. EW corrections for this process were computed in
refs.~\cite{Baur:2001ze,Arbuzov:2007db,Dittmaier:2009cr,Frederix:2018nkq}. The process receives contributions
from 13 (35) parton luminosities at NLO QCD (NLO QCD+EW),
see appendix~\ref{app:lumis} for details.

@@

The size of the EW correction is comparable to the size of the PDF uncertainty,
except at large values of transverse momentum or invariant mass, where the
former becomes larger than the latter. This fact suggests that, once included in
a global fit, EW corrections can improve the accuracy of the PDFs. In comparison
to the scale uncertainty, the size of the EW corrections remains negligible:
despite the fact that the choice of factorisation and renormalisation scales
have been devised to optimise the convergence of the perturbative expansion,
NNLO QCD corrections remain large, as expected in a process mostly initiated
by gluons. Their inclusion is therefore mandatory in a fit of PDFs. Finally,
the Monte Carlo statistical uncertainty remains negligible in comparison to the
data, PDF and scale uncertainties, and to the size of the EW correction. Our
conclusions are therefore not affected by Monte Carlo inefficiencies.

>>>>

\paragraph{Experimental measurements and process features.}
We select the single-differential invariant mass distribution of the
lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of-mass
energy of \SI{7}{\tera\electronvolt} in the high-mass region
($M_{\ell\bar\ell}>\SI{116}{\giga\electronvolt}$)~\cite{Aad:2013iua}.
We also select the single-differential rapidity distribution, $y_{\ell\bar\ell}$, in slices of
the invariant mass of the lepton pair, $M_{\ell\bar\ell}$,
measured by the CMS experiment at a centre-of-mass energy of
\SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}.
These measurements are currently included as standard in the
NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
although with appropriate kinematic cuts that remove the bins at the largest
values of invariant mass, where EW corrections become sizeable. As explained in
section~\ref{sec:pineappl-example}, 
the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
QCD contribution is $\mathcal{O}(\alphas\alpha^2)$, while the EW contribution
is $\mathcal{O}(\alpha^3)$. Our NLO QCD computation includes the
$\mathcal{O}(\alpha^2)$ and $\mathcal{O}(\alphas\alpha^2)$ contributions, while
our NLO QCD+EW computation includes the $\mathcal{O}(\alpha^2)$, 
$\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$ contributions.
Combined QCD--EW corrections occur only at NNLO, and are therefore not
considered here. EW corrections for this process were computed in
refs.~\cite{Baur:2001ze,Arbuzov:2007db,Dittmaier:2009cr,Frederix:2018nkq} (see also~\cite{Alioli:2016fum} and references therein). The process receives contributions
from 13 (35) parton luminosities at NLO QCD (NLO QCD+EW),
see appendix~\ref{app:lumis} for details.

@@

The size of the EW correction is comparable to the size of the PDF uncertainty,
except at large values of transverse momentum or invariant mass, where the
former becomes larger than the latter. This fact suggests that, once included in
a global fit, EW corrections can improve the accuracy of the PDFs. In comparison
to the scale uncertainty, the size of the EW corrections remains negligible:
despite the fact that the choice of factorisation and renormalisation scales
have been devised to optimise the convergence of the perturbative expansion,
NNLO QCD corrections remain large~\cite{Czakon:2013goa,Czakon:2014xsa,Czakon:2015owf,Czakon:2016ckf,Catani:2019iny,Catani:2019hip,Catani:2020tko}, as expected in a process mostly initiated
by gluons. Their inclusion is therefore mandatory in a fit of PDFs. Finally,
the Monte Carlo statistical uncertainty remains negligible in comparison to the
data, PDF and scale uncertainties, and to the size of the EW correction. Our
conclusions are therefore not affected by Monte Carlo inefficiencies.
